\documentclass[margin,line]{res}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{url}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
\topmargin=0in
\topskip=0in
 
\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


    
\begin{document}

\centerline{\LARGE  { \bf \href{https://saguneshgrover.com}{Sagunesh Grover} }} \hfill 
\centerline{{ Phone:}{ \bf +917011760896}, {E-mail:}{{ \href{mailto: sagunesh@gmail.com}{\bf sagunesh@gmail.com}}}\\}

\begin{resume}

\vspace{.005in}
\begin{tabular}{@{}p{3.5in}p{3in}}



\end{tabular}


\section{\sc Interests}

 Data Science, Machine Learning, Deep Learning, BigData, Information Retrieval, Applied AI, Databases

\section{\sc Academic Qualifications}
{\bf \href{http://www.srmuniversity.ac.in}{ SRM University}}, Delhi-NCR, Sonepat, Haryana, India \hfill June 2013 -- July 2017\\
%\vspace*{-.1in}
B.Tech in Computer Science and Engineering \hfill(CGPA: 7.66 \& Percentage: 76.66\%)

{\bf \href{https://www.spsrohini.com}{ Sachdeva Public School}}, Delhi. India \hfill March 2012 -- April 2013\\
 XII GRADE-CBSE \hfill(Percentage: 76.00\%)

{\bf \href{https://www.spsrohini.com/}{ Sachdeva Public School}}, Delhi. India \hfill March 2010 -- April 2011\\
 X  GRADE-CBSE \hfill(CGPA: 8.4)\\


%%%%%%%%%%%
%%%%%%%%%%%%%%%%
\section{\sc Relevant Data Science Experience}

{\bf \href{https://github.com/sagunesh/ML-CaseStudies} { Full Time DataScience Intern at AAIC Technologies Pvt. Ltd.}}\hfill {December 2017 --   Present}\\
Working on interesting real-world problems in the area of Data Science and Analytics using various Machine Learning, Computer Vision and NLP Techniques. Have been working on interesting case studies like Apparel Recommendation Engine and Personalized Cancer diagnosis and Gene Prediction. As an intern, my job was to create useful tools for the domain experts that could help them in the automation of their cumbersome processes using Machine Learning Algorithms. During the development, I used various libraries such as Pandas, NumPy, Scikit Learn, Matplotlib, Open CV and used Python programming language for the same.\\

\section{\sc Internships}
%%%%%%
{\bf 
\href{http://meity.gov.in/}{ Ministry of Electronics and Information Technology, Government of India, Electronics Niketan}},Delhi,India. \hfill{May -- July 2015}\\\\
{\em \bf \href{https://digilocker.gov.in/}{DigiLocker}}\hfill {Project Advisor : \href {https://www.linkedin.com/in/debabrata-nayak-a911397b/}{ Mr Debabrata Nayak}}
\begin{list2} %Job Description%
\item Implemented a module in OwnCloud and normalized the database for cms designed for Digilocker for reducing data redundancy.\\
\end{list2}
%%%%%%
{\em \bf \href{http://www.ecourts.gov.in/ecourts_home/}{E-court}}\hfill {Project Advisor : \href {https://www.linkedin.com/in/debabrata-nayak-a911397b/}{ Mr Debabrata Nayak}}
\begin{list2} %Job Description%
\item Developed a report filing module for E-court using cake PHP \\
\end{list2}

\section{\sc Technical Skills}
{\bf Programming and Scripting Languages}:  C, C++, Java, Python ,PHP, SQL, HTML,CSS,\\Javascipt  \\
{\bf Operating Systems}: Mac OSX, Windows, Linux\\
{\bf Tools and Frameworks}: LaTex, Numpy, Pandas, Scikit Learn, Matplotlib , Seaborn, Beautiful Soup, PyAutoGui, PhpMyAdmin, Android Studio, Spring, Hibernate, Angular Js, Node Js, JQuery, Cake PHP,  Bootstrap Framework, Jupyter Notebook,  Dreamweaver, Corel Draw \\
{\bf Version Control Tools}: Git, Bitbucket\\
{\bf Cloud Platforms}: Google Cloud Platform, AWS, Digital Ocean\\
{\bf Database Tools}:  MySql, MySqli, MS-Access, MongoDB\\\\
%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%
%%%%%%%%%%%%%%%%
\section{\sc Academic Projects}

{\bf  \href{https://github.com/sagunesh/Machine-Learning-and-Data-Science/tree/master/KNN\%20on\%20Amazon\%20Review\%20Data\%20Set}{ ML Classfier  for  Amazon Review DataSet using KNN algorithm.}}\hfill {\bf(Individual Project)}\\{\bf(March  --  July 2018)}\\
The main objective was to classify a review, determine whether the review is positive or negative using the given Amazon Review DataSet. Data Analysis and cleaning of data using various techniques like Stemming, Deduplication and Lemmatization were done. Data were preprocessed using multiple techniques like Bag of Words, TF-IDF, WORD2VEC, Avg Word2Vec and TF-Word2Vec and finally, various d dimensions vector were obtained. ‘d’ dimensions vectors were reduced to two dimensions vectors respectively using a technique called TSNE with different levels of perplexity, iterations and learning rate. KNN was applied on data, and it was visualized in two dimensions.\\


{\bf  \href{https://www.kaggle.com/saguneshgrover/habermans-survival-data-set-eda/notebook}{EDA of  Haberman's Survival Data Set.}}\hfill {\bf(Individual Project)}\\{\bf (January -- March 2018)}\\
Build a basic Machine Learning Classification model using essential Exploratory Data Analysis(EDA) techniques.\\

{\bf \href{https://github.com/sagunesh/Admob-Ad-Control} {Admob Dynamic Ad Control using Firebase}} \hfill {\bf(Individual Project)}\\{\bf (May -- November 2017)}\\
Developed a solution for managing your AdMob CTR, updating ad code on the go without updating the apps dynamically and prevent click fraud for your Android Application from malicious third party clicks\\

{\bf  \href{https://github.com/sagunesh/Large-Scale-Search-Engine}{ Large Scale Search Engine}}\hfill{\bf(Individual Project)}\\{\bf (January -- May 2017)}\\
Developed a  large-scale search engine which is a small prototype of a real-world search engine like Google. It works on millions of Wikipedia pages which are in XML format. Web Page data was preprocessed, cleaned and tokenized. Stop words were removed and stemming was done to bring the word to its base word using various stemming algorithms. An inverted index was created that will be around 7 to 9 GB. Once the query is given, it retrieves relevant ranked documents using a ranking algorithm and their titles using this index. \\\\

{\bf \href{https://github.com/sagunesh/SRM-University-Android-App}{ SRM University,Haryana Android App}}\hfill  { \bf Team size: }{(Two)} \\{\bf (November 2014 -- May 2015)}\\
Designed UI and backend of SRM University Haryana official app using which one could have the whole college experience on mobile and tablet. It was made using Angular js, Ionic framework and PhoneGap.\\

{\bf \href{https://github.com/sagunesh/SRM-University-Management-System/tree/master/online-result-module}{ SRM University Haryana Online Result Module}} \hfill {\bf(Individual Project)}\\{\bf(August -- September 2014)}\\
Developed an online examination result displaying system for the university that is used by entering a roll number and a user can get its result in pdf form.\\\\

{\bf \href{https://github.com/sagunesh/SRM-University-Management-System}{SRM University Haryana Intranet Website}} \hfill {\bf(Individual Project)}\\{\bf(June -- July 2014)}\\
Developed an online university intranet portal where students and teachers can connect, share notes, assignments and chat on a private messaging system. \\\\

{\bf  \href{https://drive.google.com/file/d/1xFzl_syoqi-URgJgDWmmM52WXdXly-XV/view}{Google Science Fair 2014}} \hfill{ \bf (Individual Project) }\\{\bf(November 2013 -- June 2014)}\\
Developed the cheapest pollution filter from waste material like(algae) to filter all harmful gases like SO\textsubscript{2},  CO\textsubscript{2} and CO out of  vehicle exhaust and convert them to O\textsubscript{2}\\






\section{\sc Awards And Achievements}
{\bf \href{https://en.wikipedia.org/wiki/Graduate_Aptitude_Test_in_Engineering} {Qualified Graduate Aptitude Test in Engineering  (Gate 2018)}} \hfill (2017 -- 2018) \\
Wrote the Graduate Aptitude Test in Engineering(GATE 2018) in the field of Computer Science and Engineering, successfully qualified the highly competitive examination among over 1,00,000  candidates and also got eligible for GATE Scholarship. \\\\
{\bf University Council Member for 2 Years Consecutively} \hfill  (2013 -- 2015)\\
Was appointed as head and member of  the University's Student Council  for the department of Computer Science and Engineering consecutively for two years \\\\
{\bf ICMAS Abacus State Champion} \hfill (2006 --  2007)\\
Became ICMAS Abacus State Champion in Delhi State for Level 1\\


\section{\sc Extracurricular Activities}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{list2}
\item I was a part of the organizing committee and organized university freshers, cultural fest and workshops.
\item Secured the {\bf 1st position} in Inter College Android App Development Competition and was qualified for finals held at IIT Delhi.
\item Got {\bf 2nd position} in Webapp development, Aqua Robo Soccer \& {\bf 3rd Position } at LFR competition at IP University.
\item Was a part of the music society and performed multiple instruments like Guitar, Electronic Keyboard and Xylophone on various occasions of University cultural fest.
\item Participated in Street Play held at SRM University, Modinagar campus.
\item Was a part of college Football team and also brought laurels to the Computer Science department in Inter Department Sports Meet.
\item Played Chess and brought honours to the Computer Science department in Inter Department Sports Meet
\item Developed a robot using Arduino which can detect the edge of an object and won the {\bf third prize} at the university on National Science Day.
\item Represented my school in Computer Symposium named edge held at Kulachi Hansraj Model School in 2010.
\item Consecutively awarded for {\bf two years} for {\bf full attendance} in school from 2006-2008.
\item Participated in painting competition under 12 years age group and secured {\bf 3rd position } in 2007
\end{list2}

\section{\sc Community Service}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\bf Nav Yuvak Jan Kalyan Sabha Delhi(Affiliated with Ministry of Youth Affairs and Sport)}\\
\begin{list2}
\item {\bf Taught   Computer Science  to under-privileged students } \hfill May -- July 2014 \\
Students were given basic knowledge about how computers work, their types, internal components were demonstrated and practically shown, taught some necessary software and their working and also a discussion about programming and future career as a software engineer was given.
\item {\bf Taught  English  to under-privileged students}   \hfill May -- July 2016 \\
Students were given basic lectures on English grammar, and held a discussion about the importance of English and answered their queries of different career paths in life.
\end{list2}

\end{resume}
\end{document}




